Experiment 4

### 2021-07-18 experiments/experiment 4/experiment 4.Rmd
remove large negative abundances
explanation in "various_useful_functions" file and at the end of the two experiment files (1 and 4)

>>>>

## negative abundance investigation

I (Owen) found that the sampling interval had an effect on the stability of the simulation. If the sampling interval was long, then in some rare cases (see below) the odesolver failed, with negative abundances occuring. I think this is due to abundances becoming very small, and then the computer having trouble with precision. I guess that when a sample is taken, the abundance is somehow altered if it is very low, probably by some rounding.

```{r}
var_expt$pars[[1]]
dd <- var_expt$ss_res[[1]]
dd1 <- filter(dd, PB_1<(-0.0001))
dd1$a_O

ss_expt_master <- ss_expt
ss_expt <- ss_expt_master[abs(ss_expt_master$a_O - 1.336984e-05)<1e-10,]

var_expt_master <- var_expt
#var_expt <- var_expt[1,]
var_expt_test <- run_ss_var_experiment()
res <- var_expt_test$ss_res[[1]]

test1 <- ss_by_a_N(ss_expt, var_expt$pars[[1]])
x <- ss_expt[2,]
param <- var_expt$pars[[1]]
get_final_states_a_N(x, param)
ssfind_parameters <- param
ssfind_simulation_sampling_interval <- 1000
## now run inside the function "get_final_states_a_N"
simres1 <- simres
ssfind_simulation_sampling_interval <- 5000
## now run inside the function "get_final_states_a_N"
simres2 <- simres  # this fails

## now run inside the function "get_final_states_a_N"
plot_dynamics(simres2)

ggplot() +
  geom_line(data = simres1$result,
             mapping = aes(x = time, y = log10(PB_1))) +
  geom_point(data = simres2$result,
             mapping = aes(x = time, y = log10(PB_1))) +
  xlim(c(0, 250000))

ccc <- simres2$result

simres2$result$PB_1
simres2$result$time

log10_a <- log10(ss_expt$a_O[1]) ## very slowly goes anoxic
#log10_a <- log10(a_Os[354]) ## very slowly goes anoxic
#log10_a <- log10(a_Os[356]) ## very very very  slowly goes anoxic
#log10_a <- log10(a_Os[357]) ## does not go anoxic

default_dynamic_model <- bushplus_dynamic_model
default_event_definition <- event_definition_1
default_event_interval <- ssfind_simulation_duration
default_noise_sigma <- 0
default_minimum_abundances <- ssfind_minimum_abundances
default_sim_duration <- ssfind_simulation_duration
default_sim_sample_interval <- ssfind_simulation_duration
#initial_pars_from <- "bush_ssfig3"

default_log10a_series <- c(log10_a, log10_a)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)

simulation_result <- sim_res_novar
every_n <- 1

chk <- sim_res_novar$result

sim_res_novar$result %>%
  ggplot() +
  geom_line(mapping = aes(x = time, y = PB_1))

#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
